---
title: "Trend Analysis"
author: "Paul Inkenbrandt"
output: html_document
---
```{r}
x <- c("gte","dplyr","rkt","zoo","lubridate")

lapply(x, require, character.only=T)
```

#Requirements#

s.resample("M", how="max")

#Import data#
```{r}
setInternet2(TRUE)
file_url <- "https://raw.githubusercontent.com/inkenbrandt/IPython/master/Sample_Na.csv"
download.file(file_url,destfile="Sample_Na",  mode="wb")
data <- read.csv("Sample_Na")

# Print date downloaded
dateDownloaded <- date()
print(paste('File downloaded ',dateDownloaded))

```

Limit data to parameter of interest. Aggregate station data into monthly or yearly datapoints.

```{r}
const <- "Sodium"

df <- filter(data, Param==const)

df <- arrange(data, StationId, SampleDate)

df <- mutate(data, type = typeof(SampleDate), month =  )


```

#Analyze Data#
We followed methods by the USGS from the publication: <a href=http://pubs.usgs.gov/sir/2012/5049/>_Methods for Evaluating Temporal Groundwater Quality Data and Results of Decadal-Scale Changes in Chloride, Dissolved Solids, and Nitrate Concentrations in Groundwater in the United States, 1988–2010_</a> to generate our trend detection tools

##Step-Trend Analysis##
"Thus, samples collected on a decadal time scale are likely to reflect an actual long-term change in concentration in the aquifer rather than a short-term change in concentration resulting from some other source of variability"

###Wilcoxon-Pratt signed-rank test###
wilcoxsign_test(zero.method = c (“Pratt”))
wilcox.test(immer$Y1, immer$Y2, paired=TRUE) 

###Fisher's Exact test###
<a href=https://stat.ethz.ch/R-manual/R-patched/library/stats/html/fisher.test.html>function documentation</a>
analyze changes in the proportion of samples that exceeded a concentration threshold

fisher.test(x, y = NULL, workspace = 200000, hybrid = FALSE,
            control = list(), or = 1, alternative = "two.sided",
            conf.int = TRUE, conf.level = 0.95,
            simulate.p.value = FALSE, B = 2000)


###Turnbull estimator for median change###
<http://cran.r-project.org/web/packages/gte/gte.pdf>

Fit <- gte(Surv(L, R, type="interval", event=2) ~ Z, data=simul, z=c(10, 20))


##Time-Series Analysis##

###Regional Kendall test###

<a href=http://cran.r-project.org/web/packages/rkt/rkt.pdf>rtk package documentation</a>
<br>
<a href=http://acwi.gov/monitoring/conference/2006/2006_conference_materials_notes/Concurrent_SessionG/G5Trends/G5_Helsel.pdf>Regional Kendall presentation by Hesel.</a>


```{r, echo=FALSE}
plot(cars)
```

