---
title: "Trend Analysis"
author: "Paul Inkenbrandt"
output: html_document
---
```{r}
x <- c("gte","coin","NADA","fitdistrplus","rkt","zoo","lubridate","tidyr","dplyr")

lapply(x, require, character.only=T)
```

#Requirements#

s.resample("M", how="max")

#Import data#
```{r}
setInternet2(TRUE)

file_url <- "https://raw.githubusercontent.com/inkenbrandt/IPython/master/Sample_Na.csv"

download.file(file_url,destfile="Sample",  mode="wb")
data <- read.csv("Sample")

# Print date downloaded
dateDownloaded <- date()
print(paste('File downloaded ',dateDownloaded))

```

Limit data to parameter of interest. Aggregate station data into monthly or yearly datapoints.

```{r}
const <- "Sodium"
time1 <- 1972
time2 <- 1973
compare <- "year"
grouping <- FALSE

df <- mutate(data, month = month(as.Date(SampleDate, format = "%m/%d/%Y")), year = year(as.Date(SampleDate, format = "%m/%d/%Y")), decade = (((year-1900)-((year-1900)%%10))+1900))


pivdates <- function(const, t1, t2, compare){
  df <- filter(df, Param==const, year>=time1, year<=time2)
  df <- arrange(df, StationId, SampleDate)
  if (compare=="year"){
    df <- filter(df, year==time1 | year==time2)
    df <- group_by(df, StationId, year)
    values <- unique(summarise(df, median = median(ResultValue)))
    values <- na.omit(spread(values, year, median, drop=TRUE))
  } else if (compare=="year-month"){
    df <- filter(df, year==time1 | year==time2)
    df <- group_by(df, StationId, month, year) 
    values <- unique(summarise(df, median = median(ResultValue)))
    values <- na.omit(spread(values, year, median, drop=TRUE))
  } else if (compare =="decade"){
    df <- filter(df, decade==time1 | decade==time2)
    df <- group_by(df, StationId, decade)
    values <- unique(summarise(df, median = median(ResultValue)))
    values <- na.omit(spread(values, decade, median, drop=TRUE))
  } else if (compare == "monthly"){
    df <- filter(df, month==time1 | month==time2)
    df <- group_by(df, StationId, month)
    values <- unique(summarise(df, median = median(ResultValue)))
    values <- na.omit(spread(values, month, median, drop=TRUE))
  } else{
    values = "none"
  } 

  return(values)
}

new_data <- pivdates(const, t1=time1, t2=time2, compare="year")


```

#Analyze Data#
We followed methods by the USGS from the publication: <a href=http://pubs.usgs.gov/sir/2012/5049/>_Methods for Evaluating Temporal Groundwater Quality Data and Results of Decadal-Scale Changes in Chloride, Dissolved Solids, and Nitrate Concentrations in Groundwater in the United States, 1988–2010_</a> to generate our trend detection tools

##Step-Trend Analysis##
"Thus, samples collected on a decadal time scale are likely to reflect an actual long-term change in concentration in the aquifer rather than a short-term change in concentration resulting from some other source of variability"

###Wilcoxon-Pratt signed-rank test###
wilcoxsign_test(zero.method = c (“Pratt”))
wilcox.test(immer$Y1, immer$Y2, paired=TRUE) 
```{r}
lent <- dim(new_data)[2]
new_data2 <- select(new_data,x = lent-1,y = lent, StationId)

res <- wilcoxsign_test(x~y, new_data2, zero.method ="Pratt")

dfg <- merge(x= new_data2, y= data, by= "StationId", all.x=TRUE)

if (grouping==TRUE){
  dfg <- group_by(df,group)
}
```


###Fisher's Exact test###
<a href=https://stat.ethz.ch/R-manual/R-patched/library/stats/html/fisher.test.html>function documentation</a>
analyze changes in the proportion of samples that exceeded a concentration threshold

fisher.test(x, y = NULL, workspace = 200000, hybrid = FALSE,
            control = list(), or = 1, alternative = "two.sided",
            conf.int = TRUE, conf.level = 0.95,
            simulate.p.value = FALSE, B = 2000)


###Turnbull estimator for median change###
<http://cran.r-project.org/web/packages/gte/gte.pdf>

#```{r}
time <- 0.15

Fit <- gte(Surv(time=time, type="left", event=2) ~ Z, data=simul, z=c(10, 20))

#```

##Time-Series Analysis##

###Regional Kendall test###

<a href=http://cran.r-project.org/web/packages/rkt/rkt.pdf>rtk package documentation</a>
<br>
<a href=http://acwi.gov/monitoring/conference/2006/2006_conference_materials_notes/Concurrent_SessionG/G5Trends/G5_Helsel.pdf>Regional Kendall presentation by Hesel.</a>


```{r, echo=FALSE}
plot(cars)
```

